{\Large SuperUROP Proposal:\\ Contextual Learning with Integrated Least Effort Knowledge Networks}

### 2016-10-06 proposal.tex
added abstract

\title{{\Large Contextual Learning with Integrated Least Effort Knowledge Networks}}
\author{Lucas E. Morales \texttt{\{lucasem\}}\\
Supervised by: Joshua Tenenbaum \texttt{\{jbt\}}}
\date{}

@@

>>>>

\title{{\Large SuperUROP Proposal:\\
Contextual Learning with Integrated Least Effort Knowledge Networks}}
\author{Lucas E. Morales \texttt{\{lucasem\}}\\
Supervised by: Joshua Tenenbaum \texttt{\{jbt\}}}
\date{}

@@

\begin{abstract}
  In the field of artifical intelligence, there are many remarkable
  mechanisms for learning in a specified manner, but these lack the
  generality that is apparent in human cognition. Most learning mechanisms
  are either inherently specialized or have a flat knowledge base that makes
  them only useful when confined to a single domain. This is flawed as a
  model of cognition because it reduces capability of both handling very
  complex problems and specializing in multiple domains. This project is to
  design a contextual knowledge system and to augment learning mechanisms to
  utilize it in a manner that reduces the intractability of hard problems by
  creating implicit relationships between knowledge in a scale-free network.
\end{abstract}
